\documentclass[11pt]{NSFamsart}
\usepackage{latexsym,amsfonts,amsmath,epsfig,multirow}
\usepackage{stackrel,tabularx,mathtools,enumitem,xspace}
\usepackage[dvipsnames]{xcolor}
\usepackage[numbers]{natbib}
\usepackage{hyperref,accents}
\usepackage[margin=1in]{geometry}

% This package prints the labels in the margin
%\usepackage[notref,notcite]{showkeys}


%\pagestyle{empty}
\thispagestyle{plain}
\pagestyle{plain}

%\headsep-0.6in
%\headsep-0.45in

\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\textheight9in
%\textheight9.1in

\begin{document}
%\setlength{\leftmargini}{2.5ex}

\centerline{\textbf{\Large Budget Justification}}

\subsection*{Salaries and Wages}

Fred J. Hickernell, the PI is budgeted at two months of summer salary per year.  He will lead 
the research.  This includes leading the weekly research seminar and  meeting individually with the 
students and visitors involved in this project.

The proposed salary for the graduate research assistant is vital, not only for the training of students, 
but also as brainpower to contribute to the construction, analysis, and implementation of our new 
algorithms.  The graduate research assistant will also help to mentor the REU students.

The undergraduate salaries are for two REU students per summer.  This research experience helps 
prepare students for further study and STEM careers by exposing them to the solving of problems 
whose answers are yet unknown.

\subsection*{Fringe Benefits}
Fringe benefit rate is 23.8\% for academic year salary and 7.9\% for the summer month
salary.

\subsection*{Travel}
The PI and co-PI will travel to several conferences each year to disseminate their work and to learn 
what others have discovered.  These include, e.g., annual meetings of the major mathematical and 
statistical societies, specialized meetings in Monte Carlo methods and related fields, and regional 
conferences. 

We often take our students to conferences with us so that they may have the experience of 
presenting their work and networking with the academic community.  The REU students are always 
encouraged to attend conferences to present their work. 

\subsection*{Other Direct Costs - Tuition}
The current tuition rate is \$1,470 per credit hour. Amount requested is 
\$1,470 $\times$ 9 credit hours per year = \$13,200 per year.

\subsection*{Indirect Costs}
Our federally negotiated rate is 53\% of modified total direct costs.

\subsection*{Inflation}A 4\% annual increase applies to all categories

\end{document} 